%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%---------------------------------------------------------

\begin{cventries}
\cventry
{Public Relations Team Member} % Affiliation/role
{Computer Science Student Association in NYCU} % Organization/group
{} % Location
{May. 2022 - Jul. 2023} % Date(s)
{
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {Wrote articles to advocate fundamental knowledge within the field of computer science. {\href{https://medium.com/@csunion.nctu}{ \faMedium\acvHeaderIconSep\@Medium}}}
    \item {Organized a Christmas dance party and a Computer Science Night, seeking sponsorship from businesses.}
  \end{cvitems}
}


%---------------------------------------------------------
  \cventry
    {Treasurer} % Affiliation/role
    {NYCU Music Game Club} % Organization/group
    {} % Location
    {Jul. 2022 - Jul. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Managed the club's budget, ensuring that financial resources are allocated appropriately and transparently.}
        \item {Planned a cross-school club exchange event in collaboration with Tunghai University.}
      \end{cvitems}
    }

%---------------------------------------------------------

\cventry
{Member} % Affiliation/role
{NYCU Pop Dance club} % Organization/group
{} % Location
{Sep. 2022 - Now} % Date(s)
{
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {Developed stage presence and confidence through dance performances and events.}
    \item {Collaborated closely with team members within a dance society, fostering teamwork and enhancing interpersonal skills.}
    \item {Demonstrated effective time management skills by successfully balancing dance rehearsals with other commitments.}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}